\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-16 terminology.tex
restore a footnote

\resume{enumerate}
	\item {\bf Thread}:
		One participating agent in a concurrent program, which executes code sequentially, with the potential to be interleaved with the execution of other threads in the system.
		Each thread has a unique numeric identifier (TID).
	\item {\bf Involuntary preemption}:
		A context switch from one thread to another caused by a nondeterministic event, such as a timer tick or device interrupt. The systematic testing framework must control all sources of nondeterminism. In this work, we focus only on timer-driven thread switches.
	\item {\bf Voluntary reschedule}:
		A context switch from one thread to another which the guest kernel performed automatically, not triggered by nondeterministic events and/or Landslide but rather as part of its normal execution.

		Voluntary reschedules may or may not be necessary for the kernel to behave correctly at all (for example: switching away from an exiting thread or from a thread blocked on \texttt{wait} is necessary, but switching to a newly-forked thread is not). Involuntary preemptions, however, are never necessary for correct kernel behaviour.
		See Section~\ref{sec:components-arbiter}.
\suspend{enumerate}

>>>>

\resume{enumerate}
	\item {\bf Thread}:
		One participating agent in a concurrent program, which executes code sequentially, with the potential to be interleaved with the execution of other threads in the system.
		Each thread has a unique numeric identifier (TID).
	\item {\bf Involuntary preemption}:
		A context switch from one thread to another caused by a nondeterministic event, such as a timer tick or device interrupt. The systematic testing framework must control all sources of nondeterminism. In this work, we focus only on timer-driven thread switches.
	\item {\bf Voluntary reschedule}:
		A context switch from one thread to another which the guest kernel performed automatically, not triggered by nondeterministic events and/or Landslide but rather as part of its normal execution.\footnote{
		Voluntary reschedules may or may not be necessary for the kernel to behave correctly at all (for example: switching away from an exiting thread or from a thread blocked on \texttt{wait} is necessary, but switching to a newly-forked thread is not). Involuntary preemptions, however, are never necessary for correct kernel behaviour.}
		See Section~\ref{sec:components-arbiter}.
\suspend{enumerate}
